Kids Basic Mutual Exclusivity

### 2019-04-16 stats/kids_basic_me.Rmd
first pass model and me by age

```{r}
d_model <- d %>%
    filter(trial != "train1",
         trial != "train2")%>%
  mutate(age_num = scale(age_num))

@@

ranef_plot <- as_tibble(ranef$familiar, rownames = "familiar")%>%
  mutate(grand_intercept = fixef%>%filter(term=="Intercept")%>%pull(Estimate),
         grand_slope = fixef%>%filter(term=="age_num")%>%pull(Estimate))%>%
  group_by(familiar) %>%
  expand(Estimate.Intercept,Estimate.age_num,grand_intercept,grand_slope,age = scale(d$age_num))%>%
  mutate(y = plogis(grand_intercept + Estimate.Intercept+(Estimate.age_num+grand_slope)*age), 
         age = age+mean(d$age_num))%>%
  left_join(aoa_ratings)%>%
  ungroup()%>%
  mutate(familiar = fct_reorder(factor(familiar), mean_aoa))

>>>>

```{r}
d_model <- d %>%
    filter(trial != "train1",
         trial != "train2")%>%
  mutate(age_num = age_num - mean(age_num))

@@

ranef_plot <- as_tibble(ranef$familiar, rownames = "familiar")%>%
  mutate(grand_intercept = fixef%>%filter(term=="Intercept")%>%pull(Estimate),
         grand_slope = fixef%>%filter(term=="age_num")%>%pull(Estimate))%>%
  group_by(familiar) %>%
  expand(Estimate.Intercept,Estimate.age_num,grand_intercept,grand_slope,age = d$age_num - mean(d$age_num))%>%
  mutate(y = plogis(grand_intercept + Estimate.Intercept+(Estimate.age_num+grand_slope)*age), 
         age = age+mean(d$age_num))%>%
  left_join(aoa_ratings)%>%
  ungroup()%>%
  mutate(familiar = fct_reorder(factor(familiar), mean_aoa))
